%------------------------
% Resume - Yiwen Wei
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Yiwen Wei}} & Email: \href{mailto:yiwenwei@andrew.cmu.edu}{yiwenwei@andrew.cmu.edu}\\
  \href{https://yiwen.bio}{Portfolio: yiwen.bio} & Mobile:~~~+1-626-649-1408 \\
  \href{https://www.linkedin.com/in/yiwenwei}{LinkedIn: linkedin.com/in/yiwenwei} \\
  \href{https://github.com/yiwenwei-dot}{Github: ~~github.com/yiwenwei-dot} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University, Silicon Valley}{Mountain View, CA}
      {Master of Science in Software Management ~\textbar~ GPA: 3.89/4.0}{Aug 2025 -- Dec 2026}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Product Management, Problem Discovery and Definition, Product \& Business Modeling, Solution Strategy \& Marketing, Process \& Project Management, Software Engineering Management, Organizational Behavior, Business of Software Industry, Applied AI, Architecture \& Programming Principles, Venture Governance, etc.}}}
    \resumeSubheading
      {City Institute, Dalian University of Technology}{Liaoning, China}
      {Bachelor of Information Management and Information Systems ~\textbar~ GPA: 3.94/4.0}{}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Honors:} Major Rank Top 1 (Accelerated: 4-year program in 3 years); National Scholarship (Top 1\%); Merit Student of Liaoning Province (Top 0.3\%)}}}
  \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Product}{~~~~~~~~~~Product Strategy, User/SME Interview, Strategy Consulting \& Analysis, Stakeholder Analysis, Journey Mapping, JTBD Framework, Value Proposition Design}
	\resumeSubItem{Technical}{~~~~~~~\textit{SWE:} Full-Stack Web Development (Claude-Assisted), Python, IoT, Database ~\textbar~ \textit{AI \& CV:} YOLO, OpenCV, AI Model Deployment, Data Labeling \& Training ~\textbar~ \textit{Simulation \& 3D:} CARLA, Unreal Engine, Blender, RoadRunner ~\textbar~ \textit{Design:} UI/UX Design}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Claude Code, Notion, Miro, VS Code, LucidSpark, Canva, Gamma, Figma Make, Git, etc.}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Product Engineer}{San Francisco, CA}
    {TurtleTalk -- Founders, Inc. Accelerator}{}
    \resumeItemListStart
        \resumeItem{Product Discovery}
          {Led product discovery through Jobs-to-Be-Done (JTBD) research and value proposition design, translating user insights into a clear product strategy aligned with market needs.}
        \resumeItem{System Architecture}
          {Defined system architecture and data flows, making technical decisions on stack selection, API design, and integration patterns to support rapid prototyping.}
        \resumeItem{Prototype Delivery}
          {Shipped a functional prototype website within 4 weeks, coordinating cross-functional efforts from concept through deployment at the Founders, Inc. accelerator in San Francisco, CA.}
      \resumeItemListEnd

\vspace{-5pt}
    \resumeSubheading{Computer Science Teacher}{Yichang, China}
    {Yichang Experimental Primary School (Top Public Primary School in Yichang City)}{}
    \resumeItemListStart
        \resumeItem{AI Educator Excellence}
          {Achieved Outstanding Rating (top 10\%) in a nationwide AI educator training program with 1,500+ participants.}
        \resumeItem{EdTech Innovation}
          {Implemented a Dual-Teacher Instruction Platform integrated with IoT devices, improving student engagement by 30\%; showcased via a nationwide teacher livestream.}
        \resumeItem{Teacher Training}
          {Conducted live training for 2,000+ teachers in a city-level IT Training Program on technology integration strategies.}
        \resumeItem{Competition Coaching}
          {Recognized as provincial-level Outstanding Competition Coach; in 2022, guided two students to national awards in creative coding (two out of merely four primary school nominations in Hubei Province).}
      \resumeItemListEnd

\vspace{-5pt}
    \resumeSubheading
		{English Teacher}{Beijing, China}
		{Rise Subject English, Beijing Flagship School (Listed Company)}{}
		\resumeItemListStart
        \resumeItem{Teaching Excellence}
          {Awarded 3rd place out of 90+ instructors in the Flagship School Annual Teaching Competition.}
        \resumeItem{Mentorship}
          {Mentored new teachers on lesson preparation and classroom management techniques.}
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Selected Projects}
\resumeSubHeadingListStart

\resumeSubItem{\href{https://turtletalk.io}{TurtleTalk -- End-to-End Product Development} \textit{(Feb 2026 -- Mar 2026 $\vert$ San Francisco, CA)}}{Led product discovery through JTBD research and value proposition design, defined system architecture and data flows, and shipped a functional prototype website during 4 weeks at accelerator Founders, Inc.}
\vspace{2pt}

\resumeSubItem{\href{https://share.descript.com/view/YHdNzBe8q7b}{Autonomous Driving Simulation Workshop (CMU)} \textit{(Dec 2025 $\vert$ Mountain View, CA)}}{Co-led a workshop open to the general public on CARLA-based autonomous driving simulation, introducing fundamentals of perception systems, sensors, path planning, and 3D environment modeling integrated with Unreal Engine, culminating in a simulated driving experience as the coursework final report for Software Engineering Management.}
\vspace{2pt}

\resumeSubItem{\href{https://www.openinnolab.org.cn/pjlab/project?id=63d8da549bd420342591c7d1\&sc=63797fc77300080be72c0525}{Head-Down Pedestrian Detection System (Computer Vision)} \textit{(Jan 2023 -- Feb 2023 $\vert$ Yichang, China)}}{Built a real-time object detection application using YOLO, PyTorch, and OpenCV to detect pedestrians using phones at crosswalks and trigger warning signals to improve road safety.}
\vspace{2pt}

\resumeSubItem{Stakeholder \& Macro Environment Analysis for EdTech Case Study (CMU) \textit{(Sep 2025 -- Nov 2025 $\vert$ Mountain View, CA)}}{Conducted stakeholder mapping, macro environment analysis, and journey mapping for an EdTech company as part of the Integrated Thinking for Innovation course.}
\vspace{2pt}

\resumeSubItem{Subject Matter Expert Interviews on EdTech in U.S. and China (CMU) \textit{(Oct 2025 $\vert$ Mountain View, CA)}}{Interviewed subject matter experts to compare AI education product needs across U.S. and Chinese markets; synthesized insights into product recommendations.}

\resumeSubHeadingListEnd

\vspace{-5pt}
%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {\textbf{2nd Place} -- Lablab.ai Hackathon Google DeepMind Challenge \hfill \textit{San Francisco, CA}}
\vspace{-5pt}
\item {\textbf{3rd Place} -- HackStorm AIoT Hackathon \hfill \textit{Mountain View, CA}}
\vspace{-5pt}
\item {\textbf{Invited Judge} -- Yichang Student Computer Creation Competition \hfill \textit{Yichang, China}}
\vspace{-5pt}
\item {\textbf{First Prize (x2)} -- Hubei Provincial Teacher Education and Information Exchange Activity \hfill \textit{Hubei, China}}
\vspace{-5pt}
\item {\textbf{First Place} -- Yichang Gamified Teaching Resource Development Competition \hfill \textit{Yichang, China}}
\vspace{-5pt}
\item {\textbf{Outstanding Certificate} -- Shanghai AI Laboratory Educator Training \hfill \textit{Shanghai, China}}
\end{description}

\vspace{-5pt}
\section{Test Scores}
\begin{description}[font=$\bullet$]
\item {GRE: 330 (V162/Q168/AW3.5), 2024}
\end{description}

\end{document}
